\documentclass[11pt]{article}
\textwidth 7.5in
\textheight 10in
\oddsidemargin -.5in
\evensidemargin -.5in
\topmargin -1in    
\usepackage{graphics}        
\usepackage{graphicx}
\usepackage{amsmath,amsthm,amscd,amssymb}
\usepackage{latexsym}
\usepackage{upref}
\begin{document}
\newcommand{\dsp}{\displaystyle}
\newcommand{\ihat}{{\bf{i}}}
\newcommand{\jhat}{{\bf{j}}}
\newcommand{\khat}{{\bf{k}}}
\newcommand{\Fhat}{{\bf{F}}}
%\pagestyle{headings}
%\markright{MATH 1120 Lab Worksheet \#1}

\thispagestyle{empty}

\noindent
\sffamily
\begin{center}
\rule{7.5in}{2pt}

\vspace{.2in}

\begin{tabular}{p{4in}p{3.5in}}
MATH 2825

\vspace{.2in}

Computer Lab \#3
& 
NAME:  $_{\rule{2.5in}{1pt}}$

\vspace{.2in}

Due Thursday November 3rd 2022 by 11:59 P.M.
\\*[.2in]
\end{tabular}
\rule{7.5in}{2pt}

\vspace{.1in}
All work is to be done in a mathematica or jupyter notebook. \\
 Please refer to the blackboard site for commands and examples. \\
 Submissions must be made electronically on Blackboard. \\
   You will be graded on the output that I am able to generate from your commands.\\
\bf Please delete all output before submitting.
\end{center}
\begin{tabular}{*{26}{|c}|}\hline
A&B&C&D&E&F&G&H&I&J&K&L&M&N&O&P&Q&R&S&T&U&V&W&X&Y&Z\\ \hline
1&2&3&4&5&6&7&8&9&10&11&12&13&14&15&16&17&18&19&20&21&22&23&24&25&26\\ \hline
\end{tabular}

\begin{enumerate}
\item Let $a$ be the digit corresponding to your first initial in the table above.  Consider the function 
\[f(x)=\sqrt{\frac{x^4-x+a}{x^4+x+a}}\]
\begin{enumerate}
\item Graph the function on an appropriate interval.
\item Compute the derivative of the function.\label{a}
\item Simplify the derivative and say in words what changed from part \ref{a}.
\item Find the points on the graph where the function $f$ has a horizontal tangent.\label{c}
\item Graph $f$ and $f'$ on the same axis.  Explain in words why or why not your graphs are consistent with the answer found in part \ref{c}
\end{enumerate}




\item Consider the curve (Tschirnhausen Cubic), where $a$ is as defined above,
\[
y^2=x^3+a x^2.
\]
\begin{enumerate}
\item Graph the equation.  I would suggest ContourPlot for Mathematica, plot\_implicit for sympy python, or breaking into two pieces.  Describe in words what you see.
\item Where does the graph have horizontal tangents?
\item Where does the graph have vertical tangents?
\item Explain in words how the picture supports your mathematics.

\end{enumerate}
\item Consider the function, 
\[
g(x)=e^{-x^2/\left(2\sigma^2\right)}.
\]
\begin{enumerate}
\item Start by setting $\sigma=a$.  Find the asymptote, maximum value and inflection points.  Plot the function and the points identified.\label{lots}
\item Change $\sigma=2a$.  Describe in words the changes you observe to all values found in \ref{lots}.\label{abb}
\item Graph at least four different values of $\sigma$ to verify your predictions in \ref{abb}.
\end{enumerate}
\end{enumerate}
\end{document}





